---
title: "From Regression to Moderation"
author: "Keon-Woong Moon"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,comment=NA,message=FALSE,
                      warning=FALSE,
                      fig.with=6,fig.asp=0.618,
                      out.width="70%",fig.align="center")
```

In statistical modelling, regression analysis is a set of statistical process for estimating the relationships among variables. [https://en.wikipedia.org/wiki/Regression_analysis] In general, regression analysis can be used to identify the explanatory variables that are related to a response variable, to describe the form of the relationships involved, and to provide an equation for predicting the response variable from the explanatory variables. In this introduction, I do not explain the fundamentals of regression analysis. Instead I will show you the concept of regression analysis and how to use R to perform the analysis with R and how to use the results to get the regression equation.


## Simple Linear Regression Model

In simple linear regression, there is one response(dependent) variable and one explanatory(independent) variable. 


```{r two figs,out.width="50%",fig.align="default",fig.show='hold',fig.cap="Figure 1.Concept(left) and Statistical Model(right) of Simple Linear Regression"}
require(processR)
require(predict3d)
pmacroModel(0)
statisticalDiagram(0)
```



```{r,echo=FALSE}
require(knitr)
df=data.frame(formula="Y ~ X", equation="Y ~ b*X")
colnames(df)=c("R formula", "Equation")
kable(df)
```
