---
title: "Introduction to R package processR"
subtitle: "From Regression to Moderation"
author: "Keon-Woong Moon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,comment=NA,message=FALSE,
                      warning=FALSE,
                      fig.with=6,fig.asp=0.618,
                      out.width="70%",fig.align="center")
```

In statistical modelling, regression analysis is a set of statistical process for estimating the relationships among variables[https://en.wikipedia.org/wiki/Regression_analysis]. In general, regression analysis can be used to identify the explanatory variables that are related to a response variable, to describe the form of the relationships involved, and to provide an equation for predicting the response variable from the explanatory variables. In this introduction, I do not explain the fundamentals of regression analysis. Instead I will show you the concept of regression analysis and how to use R to perform the analysis with R and how to use the results to get the regression equation.


## Simple Linear Regression Model

In simple linear regression, there is one response(dependent) variable and one explanatory(independent) variable. 


```{r }

require(processR)
require(predict3d)
statisticalDiagram(1)

```

```{r,echo=FALSE,results='asis'}
require(ztable)
df1=data.frame(Rcode="Y ~ X",Equation= " Y ~ b * X")
ztable(df1,type="html",include.rownames=FALSE,tablewidth=1)
```


 
